---
title: "DSC 200 Lab Project -Term 2232"
date: "`r Sys.Date()`"
output: github_document
---

**Student Name:<" hadi-alshammari ">**

**Student ID:<2210002975>**


**Deadline:** 23:59 on Sunday, 19 May 2024

**Total Points:** 20


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
library(dplyr)
```


## Tasks

`1. (2 points)
```{r}
seattlepets %>%
distinct (species)
```
Write your narrative here




`2. (2 points)

```{r}
seattlepets %>%
  ncol()
```
Write your narrative below



`3. (2 points)
```{r}
seattlepets %>%
select (species) %>%
  count(species , sort = TRUE)
```
Write your narrative here


`4. (2 points)
```{r}
seattlepets %>% 
  select(animal_name) %>%
  count(animal_name , sort = TRUE)
```
Write your narrative here


`5. (2 points)
```{r}
seattlepets %>%
filter(species == "Pig") %>%
  arrange(animal_name)
```
Write your narrative here




`6. (2 points)
```{r}
seattlepets %>%
  filter(species == "Goat") %>%
  select(animal_name , primary_breed) %>%
  arrange(animal_name)
  
``` 
Write your narrative here





`7. (2 points)
```{r}
seattlepets %>%
  mutate(pet = animal_name , species) %>%
  select(license_number , pet) %>%
  arrange(pet)

```
Write your narrative here



`8. (2 points)
```{r}
ggplot(seattlepets,aes(x=species))+
  geom_bar();
```
Write your narrative here




`9. (2 points)
```{r}
top_10_names <- seattlepets %>% 
filter(animal_name %in% c( "Lucy"  , "Charlie" , "Luna" , "Bella" , "Max"    , 
                           "Daisy" , "Molly"   , "Jack" , "Lily"  , "Stella" ))
top_10_names
```
`a.	What does the above code chunk do?

**display a New column as "top_10_names" contains the top 10 name**

`b. Plot the counts of the pet names (animal_name) in top_10_names

```{r}
 seattlepets %>%
  filter(animal_name %in% c( "Lucy"  , "Charlie" , "Luna" , "Bella" , "Max"    , 
                           "Daisy" , "Molly"   , "Jack" , "Lily"  , "Stella" )) %>%
  ggplot(aes(animal_name , 
             fill = species)) + 
  geom_bar()


  
```


`10.  (2 points)

`The below code plots the proportion of dogs with a given name versus the proportion of cats with the same name. The 20 most common cat and dog names are displayed. The diagonal line on the plot is the x = y line; if a name appeared on this line, the name’s popularity would be exactly the same for dogs and cats.

```{r eval = TRUE, echo = FALSE, fig.fullwidth = TRUE}
# data prep
name_props <- seattlepets %>% 
  filter(
    !is.na(animal_name),
    species %in% c("Dog", "Cat")
    ) %>%
  group_by(species) %>% 
  count(animal_name, sort = TRUE) %>%
  mutate(prop = n / sum(n))
    
cat_name_props <- name_props %>%
  filter(species == "Cat") %>%
  rename(cat_prop = prop) %>%
  slice(1:30)

dog_name_props <- name_props %>%
  filter(species == "Dog") %>%
  rename(dog_prop = prop) %>%
  slice(1:30)
    
comb_name_props <- inner_join(cat_name_props, dog_name_props, 
                              by = "animal_name") %>%
  ungroup() %>%
  select(animal_name, cat_prop, dog_prop)
    
# create viz
ggplot(comb_name_props, aes(x = cat_prop, y = dog_prop)) +
  geom_abline(intercept = 0, 
              color = COL["lgray","full"], 
              alpha = 0.8, 
              size = 1.5) +
  geom_text_repel(aes(label = animal_name), 
                  segment.color = COL["gray","full"], 
                  seed = 291252, max.iter = 10000) +
  geom_point(color = COL["blue","full"], alpha = 0.8) +
  theme_minimal() +
  labs(x = "Proportion of cats", y = "Proportion of dogs") +
  xlim(0.002, 0.01) +
  ylim(0.002, 0.01) +
  ggimage::geom_emoji(
      image = "1f436", aes(x = 0.003, y = 0.009), size = 0.1
      ) +
  ggimage::geom_emoji(
      image = "1f431", aes(x = 0.009, y = 0.003), size = 0.1
      )
```

`What names are more common for cats than dogs? The ones above the line or the ones below the line?

`Answer here..................

**Names that are more common for cats than dogs are the ones below the line. This is because the diagonal line represents equal popularity (x = y). If a name's point is below this line, it means the proportion of cats with that name (x-axis) is greater than the proportion of dogs with that name (y-axis).**


`Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

`Answer here .............


**The relationship between the two variables is positive. This means that as the proportion of cats with a given name increases, the proportion of dogs with the same name also tends to increase. In the context of the data, this indicates that names popular for one species (cats) are also likely to be popular for the other species (dogs). There is a shared trend in naming preferences between cat and dog owners.**
